sampbias, a method for quantifying geographic sampling biases in species distribution data

### 2020-07-27 appendix_S1.Rmd
focus on Borneo appendix 1

@@

# prepare for plotting
airp <- airports %>% crop(SpatialPoints(occ[,2:1])) %>%  coordinates() %>%  data.frame() %>% mutate(type = "Airport")
cit <- cities %>% crop(SpatialPoints(occ[,2:1])) %>%  coordinates() %>%  data.frame() %>%  mutate(type = "City")
pts <- bind_rows(occ, cit, airp)

riv <- waterbodies %>% crop(SpatialPoints(occ[,2:1])) %>%  fortify() %>%  mutate(type = "River")
road <- roads %>% crop(SpatialPoints(occ[,2:1])) %>%  fortify() %>%  mutate(type = "Road")
lin <- bind_rows(riv, road)

lma <- landmass %>% crop(SpatialPoints(occ[,2:1])) %>%  fortify()

>>>>

## get a polygon of Borneo
data(landmass)

born2 <- st_read("empirical_analyses/Borneo.kml")
born2 <- sf:::st_zm(born2$geom)
born2 <- as(born2, 'Spatial')

@@

# prepare for plotting
airp <- airports %>% crop(SpatialPoints(occ[,2:1])) %>% raster::intersect(born2) %>%  coordinates() %>%  data.frame() %>% mutate(type = "Airport")
cit <- cities %>% crop(SpatialPoints(occ[,2:1])) %>% raster::intersect(born2) %>%  coordinates() %>%  data.frame() %>%  mutate(type = "City")
pts <- bind_rows(occ, cit, airp)

riv <- waterbodies %>% crop(SpatialPoints(occ[,2:1])) %>%  fortify() %>%  mutate(type = "River")
road <- roads %>% crop(SpatialPoints(occ[,2:1])) %>% raster::intersect(born2) %>%  fortify() %>%  mutate(type = "Road")
lin <- bind_rows(riv, road)

lma <- landmass %>% crop(SpatialPoints(occ[,2:1])) %>% raster::intersect(born2) %>%  fortify()
